POODLE 1.0 - To the core of your data

### 2016-01-11 poodle_project/paper/main.tex

The build and update process is implemented in Python. So the user does not have to have knowledge in 
SQL coding but only has to execute one python script and everything is done automatically. This routine 
ensures that the SQLite database and the BLAST database are always in the same state. It also makes 
the database a little bit safer, since changes can be reviewed before iserting them into the database.

@@

Our software package provides not just a database functionality for powerful and secure data storage 
and a easy-to-use interface but also a Blast (\citealp{Altschul01}) functionality. This functionality 
is implemented by a combination of Blast binaries provided by NCBI and the Biojava Api 
(\citealp{Prlic01}). There are two different Blast searches available in POODLE. On one hand, there 
is a remote Blast search on the NCBI server. And on the other hand, there is a local Blast search. 
The remote Blast search is not a fully functional copy of the NCBI web service but can used to 
perform a quick and simply search against NCBI databases, e.g. Swissprot (\citealp{Doni01}). But we do not recommend to 
overuse that because too many requests may cause a blacklisting by NCBI.

@@

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Bag01} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Bag01} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text.

Table~\ref{Tab:01} shows that Text Text Text Text Text  Text Text
Text Text Text Text. Figure~2\vphantom{\ref{fig:02}} shows that
the above method Text Text. Text Text Text  Text Text Text Text
Text Text. Figure~2\vphantom{\ref{fig:02}} shows that the above
method Text Text. Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     please remove the " % " symbol from \centerline{\includegraphics{fig01.eps}}
%     as it may ignore the figures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

(Table~\ref{Tab:01}) Text Text Text Text Text Text  Text Text Text
Text Text Text Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Bag01} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Bag01} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Bag01} might want to know about  text text text text

\begin{enumerate}
\item this is item, use enumerate
\item this is item, use enumerate
\item this is item, use enumerate
\end{enumerate}

Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows\vadjust{\pagebreak} that the
above method  Text Text Text Text Text Text Text Text Text Text
Text Text.  \citealp{Bag01} might want to know about text
text text text Text Text Text Text Text Text  Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Bag01} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text\break Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text\vspace*{-10pt}

@@

Text Text Text Text Text Text  Text Text.  \citealp{Bag01} might want to know about  text
text text text\vspace*{-12pt}

>>>>

The build and update process is implemented in Python. So the user does not have to have knowledge in 
SQL coding but only has to execute one python script and everything is done automatically. This routine 
ensures that the SQLite database and the BLAST database are always in the same state. It also makes 
the database a little bit safer, since changes can be reviewed before inserting them into the database.

@@

Our software package provides not just a database functionality for powerful and secure data storage 
and a easy-to-use interface but also a Blast (\citealp{Altschul01}) functionality. This functionality 
is implemented by a combination of Blast binaries provided by NCBI and the Biojava Api 
(\citealp{Prlic01}). There are two different Blast searches available in POODLE. On one hand, there 
is a remote Blast search on the NCBI server. And on the other hand, there is a local Blast search. 
The remote Blast search is not a fully functional copy of the NCBI web service but can used to 
perform a quick and simply search against databases provided by NCBI, e.g. Swissprot (\citealp{Doni01}). But we 
do not recommend to overuse that because too many requests may cause a blacklisting by NCBI. This 
remote Blast routine is mainly for the insertion of a new entry. The idea is to check whether there 
are information about the new sequence. The local Blast routine does everything someone would 
expect from a Blast search but against the local database, hence local Blast.

@@

@@

@@
